---
name: Alberson
surname: Miranda
position: "Data Science | Analytics | Economics"
address: "Vitória, Brazil"
www: "datamares.netlify.app/"
email: "albersonmiranda@hotmail.com"
github: albersonmiranda
linkedin: albersonmiranda
headcolor: "414141"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Industry Positions

```{r industry}
tribble(
  ~role, ~company, ~loc, ~dates, ~details,
  "Advisor", "Banestes SA", "Vitória, Brazil", "Jul. 2024 - Present",
  list(
    "Develop, monitor, and fine-tune expected credit loss models (IFRS9) using statistical and machine learning techniques.",
    "Work within the Credit Risk Modeling Office.",
    "Utilize: R, Python, Google Cloud Platform, MS SQL Server, VSCode, Jira, Bitbucket."
  ),
  "Advisor", "Banestes SA", "Vitória, Brazil", "Jan. 2020 - Jun. 2024",
  list(
    "Trained, evaluated, and interpreted statistical models and experiments to support data-driven decision-making and product development within the Credit Innovation Office."
  ),
  "Head of Collection", "Banestes SA", "Vitória, Brazil", "Apr. 2014 - Dec. 2019",
  list(
    "Developed and implemented collection strategies that **improved recovery rates by 12% annually.**",
    "Applied econometric techniques for optimized collection and budget planning."
  ),
  "Loan Officer", "Banestes SA", "Vitória, Brazil", "Jul. 2008 - Mar. 2014",
  list(
    "Managed and processed loan applications, ensuring compliance and customer satisfaction." # Added a detail for this role.
  )
) %>%
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r education}
tribble(
  ~degree, ~uni, ~loc, ~dates, ~details,
  "PhD in Economics", "Universidade Federal do Espírito Santo", "Vitória, Brazil", "Jan. 2024 - Present",
  list(
    "Research Area: Regularized Hierarchical Time Series Econometrics.",
    "Relevant coursework: Input-Output Analysis, Evaluation of Public Policies, Multivariate Methods for Data Analysis."
  ),
  "M.Sc in Economics", "Universidade Federal do Espírito Santo", "Vitória, Brazil", "Jan. 2022 - Dec. 2023",
  list(
    "Thesis: \"Machine Learning Methods for Optimal Reconciliation of Hierarchical and Grouped Time Series.\"",
    "Relevant coursework: Advanced Microeconomics, Advanced Macroeconomics, Advanced Econometrics, Time Series Analysis, Economics of Information, Culture and Knowledge."
  ),
  "B.Sc in Mathematics", "Instituto Federal do Espírito Santo", "Vitória, Brazil", "Feb. 2018 - Dec. 2023",
  list(
    "Coursework included: Real Analysis, Number Theory, Algebra, Axiomatic Geometry, Linear Algebra, Statistics, and Complex Calculus."
  ),
  "B.Sc in Economics", "Universidade Federal do Espírito Santo", "Vitória, Brazil", "Feb. 2007 - Dec. 2013",
  list(
    "Coursework included: Microeconomics, Macroeconomics, Econometrics."
  )
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```

# Software

da Silva Miranda A (2025). _fio: Friendly Input-Output Analysis_. doi:10.32614/CRAN.package.fio <https://doi.org/10.32614/CRAN.package.fio>, R package version 0.1.6, <https://CRAN.R-project.org/package=fio> (author, maintainer).

Wilke C, Thomason A, Reimert M, Kosenkov I, Barrett M (2025). _rextendr: Call Rust Code from R using the 'extendr' Crate_. R package version 0.3.1.9001, <https://extendr.github.io/rextendr/> (contributor).

da Silva Miranda A (2025). _R Tools PPA: Repository for Posit's Rstudio, Positron and Quarto for .deb and .rpm packages_. GitHub repository, https://github.com/albersonmiranda/r_tools_ppa (author, maintainer).

# Additional Experience

Translator of the portuguese version of the book _"R for Data Science"_ by Hadley Wickham and Garrett Grolemund (https://pt.r4ds.hadley.nz/).
