---
name: Alberson
surname: Miranda
position: "Data Science | Analytics | Economics"
address: "Vitória, Brazil"
www: "datamares.netlify.app/"
email: "albersonmiranda@hotmail.com"
github: albersonmiranda
linkedin: albersonmiranda
headcolor: "414141"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Industry Positions

```{r industry}
tribble(
  ~role, ~company, ~loc, ~dates, ~details,
  "Advisor", "Banestes SA", "Vitória, Brazil", "Jul. 2024 - Present",
  list(
    "Credit Risk Modelling office.",
    "Build, monitor and tune risk related models through statistics and machine learning (e.g., probability of default, loss given default, forward looking)",
    "Stack: R, MS SQL Server, Python, VSCode, Jira, Bitbucket.",
    ""
  ),
  "Advisor", "Banestes SA", "Vitória, Brazil", "Jan. 2020 - Jun. 2024",
  list(
    "Analytics in Credit Innovation Office.",
    "Train, evaluate and interpret models, tests and statistical experiments to assist in the decision making and data-related products.",
    ""
  ),
  "Head of Collection", "Banestes SA", "Vitória, Brazil", "Apr. 2014 - Dec. 2019",
  list(
    "Developed strategies and managed contracts.",
    "Applied several econometric techniques for collection and budget planning.",
    ""
  ),
  "Loan Officer", "Banestes SA", "Vitória, Brazil", "Jul. 2008 - Mar. 2014",
  list(
    #""
  )
) %>%
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r education}
tribble(
  ~degree, ~uni, ~loc, ~dates, ~details,
  "PhD in Economics", "Universidade Federal do Espírito Santo", "Vitória, Brazil", "Jan. 2024 - Present",
  list(
    "Research area: Hierarchical Time Series Econometrics.",
    "Studied units include Input-Output Analysis, Evaluation of Public Policies, Multivariate Methods for Data Analysis.",
    ""
  ),
  "M.Sc in Economics", "Universidade Federal do Espírito Santo", "Vitória, Brazil", "Jan. 2022 - Dec. 2023",
  list(
    "Thesis: Machine Learning Methods for Optimal Reconciliation of Hierarchical and Grouped Time Series",
    "Studied units include Advanced Microeconomics, Advanced Macroeconomics, Advanced Econometrics, Time Series Analysis and Economics of Information, Culture and Knowledge.",
    ""
  ),
  "B.Sc in Mathematics", "Instituto Federal do Espírito Santo", "Vitória, Brazil", "Fev. 2018 - Dec. 2023",
  list(
    #"Thesis: Education-Income Relations in Espírito Santo.",
    #"Studied units include Real Analysis, Number Theory, Algebra, Axiomatic Geometry, Linear Algebra, Statistics and Complex Calculus."
  ),
  "B.Sc in Economics", "Universidade Federal do Espírito Santo", "Vitória, Brazil", "Fev. 2007 - Dec. 2013",
  list(
    #"Thesis: Solow Versus Endogenous Growth Models."
  )
) %>%
  detailed_entries(degree, dates, uni, loc, details)
```

# Software

da Silva Miranda A (2025). _fio: Friendly Input-Output Analysis_. doi:10.32614/CRAN.package.fio <https://doi.org/10.32614/CRAN.package.fio>, R package version 0.1.6, <https://CRAN.R-project.org/package=fio> (author, maintainer).

Wilke C, Thomason A, Reimert M, Kosenkov I, Barrett M (2025). _rextendr: Call Rust Code from R using the 'extendr' Crate_. R package version 0.3.1.9001, <https://extendr.github.io/rextendr/> (contributor).

da Silva Miranda A (2025). _R Tools PPA: Repository for Posit's Rstudio, Positron and Quarto for .deb and .rpm packages_. GitHub repository, https://github.com/albersonmiranda/r_tools_ppa (author, maintainer).

# Other

Translator of the portuguese version of the book _"R for Data Science"_ by Hadley Wickham and Garrett Grolemund (https://pt.r4ds.hadley.nz/).
